### 2023-01-15 Poisot_et_al_2023_template_prepare_draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@a302d3933d5e797ee4af6e7e2a421e1c856a88a9 🚀

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be, see \emph{e.g.}
\textbf{Garland1999IntPhy?}), we repeat the above process
\(2\times 10^5\) times, which results in a probabilistic metaweb \(P\),
where the probability of an interaction (here conveying our degree of
trust that it exists given the inferred trait distributions) is given by
the number of times where it appears across all random draws \(N\),
divided by the number of samples. An interaction with \(P_{i,j} = 1\)
means that these two species were predicted to interact in all
\(2\times 10^5\) random draws, etc..

>>>>

Because the intervals around some trait values can be broad (in fact,
probably broader than what they would actually be), we repeat the above
process \(2\times 10^5\) times, which results in a probabilistic metaweb
\(P\), where the probability of an interaction (here conveying our
degree of trust that it exists given the inferred trait distributions)
is given by the number of times where it appears across all random draws
\(N\), divided by the number of samples. An interaction with
\(P_{i,j} = 1\) means that these two species were predicted to interact
in all \(2\times 10^5\) random draws, etc..
